MSAD_PCA_Walkthrough

### 2017-01-12 Simulation_Vignette.Rmd
Finished commenting the data generation portion. Now I'm moving to comment the individual functions themselves.

faults_ls <- list(normal = normal_switch_xts,
                  fault1A = fault1A_xts,
                  fault1B = fault1B_xts,
                  fault2A = fault2A_xts,
                  fault2B = fault2B_xts,
                  fault3A = fault3A_xts,
                  fault3B = fault3B_xts)

# Double check that faults are visible and according to plan:
# faults_ls$fault1A %>% select(x) %>% plot.ts()
# faults_ls$fault1A %>% select(y) %>% plot.ts()
# faults_ls$fault1A %>% select(z) %>% plot.ts()
# faults_ls$fault1B %>% select(x) %>% plot.ts()
# faults_ls$fault1B %>% select(y) %>% plot.ts()
# faults_ls$fault1B %>% select(z) %>% plot.ts()
# faults_ls$fault2A %>% select(x) %>% plot.ts()
# faults_ls$fault2A %>% select(y) %>% plot.ts()
# faults_ls$fault2A %>% select(z) %>% plot.ts()
# faults_ls$fault2B %>% select(x) %>% plot.ts()
# faults_ls$fault2B %>% select(y) %>% plot.ts()
# faults_ls$fault2B %>% select(z) %>% plot.ts()
# faults_ls$fault3A %>% select(x) %>% plot.ts()
# faults_ls$fault3A %>% select(y) %>% plot.ts()
# faults_ls$fault3A %>% select(z) %>% plot.ts()
# faults_ls$fault3B %>% select(x) %>% plot.ts()
# faults_ls$fault3B %>% select(y) %>% plot.ts()
# faults_ls$fault3B %>% select(z) %>% plot.ts()
faults_ls$fault1A$x %>% plot.xts()
faults_ls$fault1A$y %>% plot.xts()
faults_ls$fault1A$z %>% plot.xts()
faults_ls$fault1B$x %>% plot.xts()
faults_ls$fault1B$y %>% plot.xts()
faults_ls$fault1B$z %>% plot.xts()
faults_ls$fault2A$x %>% plot.xts()
faults_ls$fault2A$y %>% plot.xts()
faults_ls$fault2A$z %>% plot.xts()
faults_ls$fault2B$x %>% plot.xts()
faults_ls$fault2B$y %>% plot.xts()
faults_ls$fault2B$z %>% plot.xts()
faults_ls$fault3A$x %>% plot.xts()
faults_ls$fault3A$y %>% plot.xts()
faults_ls$fault3A$z %>% plot.xts()
faults_ls$fault3B$x %>% plot.xts()
faults_ls$fault3B$y %>% plot.xts()
faults_ls$fault3B$z %>% plot.xts()

######  MSAD-PCA Implementation  ##############################################
# Sys.time()
# results_ls <- mspMonitor(data = faults_ls$normal[,2:4],
#                          labelVector = faults_ls$normal[,1],
#                          trainObs = 2880,
#                          updateFreq = 1440)
# Sys.time() # 14 seconds for 720 train, 360 update; 5 seconds for 1440, 720;
# # 1 second for 2880 train (two days), and 1440 update (one day).
# 
# falseAlarmRate_SPE <- sum(results_ls$Alarms[,1] == "Alarm") /
#   nrow(results_ls$Alarms)
# falseAlarmRate_T2 <- sum(results_ls$Alarms[,2] == "Alarm") /
#   nrow(results_ls$Alarms)
# 
# faultTime <- zoo::index(faults_ls$normal[faultStart,])
# # Why don't we have 10080 - 2880 rows in the Alarm matrix??
# str(results_ls$Alarms)

>>>>

faults_ls <- list(normal = normal_switch_xts,
                  fault1A = fault1A_xts,
                  fault1B = fault1B_xts,
                  fault2A = fault2A_xts,
                  fault2B = fault2B_xts,
                  fault3A = fault3A_xts,
                  fault3B = fault3B_xts)
```

### Feature Time-series Plots
Now that we've created and stored these feature, we can use time-series plots to confirm our multi-state vision as well as quickly ascertain the fault behavior.
```{r feature_ts_plots}
# Double check that faults are visible and according to plan:
# faults_ls$fault1A %>% select(x) %>% plot.ts()
# faults_ls$fault1A %>% select(y) %>% plot.ts()
# faults_ls$fault1A %>% select(z) %>% plot.ts()
# faults_ls$fault1B %>% select(x) %>% plot.ts()
# faults_ls$fault1B %>% select(y) %>% plot.ts()
# faults_ls$fault1B %>% select(z) %>% plot.ts()
# faults_ls$fault2A %>% select(x) %>% plot.ts()
# faults_ls$fault2A %>% select(y) %>% plot.ts()
# faults_ls$fault2A %>% select(z) %>% plot.ts()
# faults_ls$fault2B %>% select(x) %>% plot.ts()
# faults_ls$fault2B %>% select(y) %>% plot.ts()
# faults_ls$fault2B %>% select(z) %>% plot.ts()
# faults_ls$fault3A %>% select(x) %>% plot.ts()
# faults_ls$fault3A %>% select(y) %>% plot.ts()
# faults_ls$fault3A %>% select(z) %>% plot.ts()
# faults_ls$fault3B %>% select(x) %>% plot.ts()
# faults_ls$fault3B %>% select(y) %>% plot.ts()
# faults_ls$fault3B %>% select(z) %>% plot.ts()
faults_ls$fault1A$x %>% plot.xts()
faults_ls$fault1A$y %>% plot.xts()
faults_ls$fault1A$z %>% plot.xts()
faults_ls$fault1B$x %>% plot.xts()
faults_ls$fault1B$y %>% plot.xts()
faults_ls$fault1B$z %>% plot.xts()
faults_ls$fault2A$x %>% plot.xts()
faults_ls$fault2A$y %>% plot.xts()
faults_ls$fault2A$z %>% plot.xts()
faults_ls$fault2B$x %>% plot.xts()
faults_ls$fault2B$y %>% plot.xts()
faults_ls$fault2B$z %>% plot.xts()
faults_ls$fault3A$x %>% plot.xts()
faults_ls$fault3A$y %>% plot.xts()
faults_ls$fault3A$z %>% plot.xts()
faults_ls$fault3B$x %>% plot.xts()
faults_ls$fault3B$y %>% plot.xts()
faults_ls$fault3B$z %>% plot.xts()
```

## Multi-State AD-PCA Implementation
We now throw all this data we've just generated into our package. CURRENT ISSUES: remove only alarmed observations, not flagged observations. Set up a replicate structure to repeat this proccess 1000 times.
```{r msad-pca}
Sys.time()
results_ls <- mspMonitor(data = faults_ls$normal[,2:4],
                         labelVector = faults_ls$normal[,1],
                         trainObs = 2880,
                         updateFreq = 1440)
Sys.time() # 14 seconds for 720 train, 360 update; 5 seconds for 1440, 720;
# 1 second for 2880 train (two days), and 1440 update (one day).

falseAlarmRate_SPE <- sum(results_ls$Alarms[,1] == "Alarm") /
  nrow(results_ls$Alarms)
falseAlarmRate_T2 <- sum(results_ls$Alarms[,2] == "Alarm") /
  nrow(results_ls$Alarms)

faultTime <- zoo::index(faults_ls$normal[faultStart,])
# Why don't we have 10080 - 2880 rows in the Alarm matrix??
str(results_ls$Alarms)
